Clean data

### 2018-03-24 01_clean-data.Rmd
Modify to work with real data

# Load data
results_file <- file.path(here(), "Data", "test_data.csv")

@@

# The first 8 rows need to be skipped because the consent question has a bunch
# of line breaks and it messes with CSV line counting. The actual responses
# start on row 9. This doesn't entirely make sense, since read_csv can read the
# line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
results_raw <- read_csv(results_file, skip = 8,
                        col_names = colnames(results_meta))

@@

  select(id = ResponseId, duration = `Duration (in seconds)`,

@@

@@

saveRDS(results, file.path(here(), "data", "results_clean.rds"))
```

>>>>

# Load data
# results_file <- file.path(here(), "data", "test_data.csv")
results_file <- file.path(here(), "private", 
                          "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")

@@

# The first 10 rows need to be skipped because the consent question has a bunch
# of line breaks and it messes with CSV line counting. The actual responses
# start on row 11. This doesn't entirely make sense, since read_csv can read the
# line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
results_raw <- read_csv(results_file, skip = 10,
                        col_names = colnames(results_meta))

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- readLines(file.path(here(), "data", "codes_to_exclude.txt")) %>% 
  as.numeric()

# Clean everything

@@

  select(id = ResponseId, confirmation_code = mTurkCode, duration = `Duration (in seconds)`,

@@

  # This person contacted me separately to say that they accidentally did the first
  # attention check wrong, but that they did pay attention: 6518634
  mutate(attention1_correct = ifelse(confirmation_code == 6518634,
                                     TRUE, attention1_correct)) %>% 
  filter(!(confirmation_code %in% codes_to_exclude)) %>%

@@

saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csv(results, file.path(here(), "data", "results_clean.csv"))
```
